Commutative character sheaves and geometric types for supercuspidal representations

### 2017-04-20 Geometric types.tex
small stuff

Let $j : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j\times 1_G : G\der \to G\times G$ by $i\der(h) = (j(h),1_G)$. \todo{There's some kind of typo here....}
For $(\cs{L},\mu,\nu)\in \CSab'(G)$, $(j\times 1_G)^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism.
This defines a functor
\[
\begin{array}{rcl}
\CSab'(G) &\to& \CSab(G) \\
(\cs{L},\mu,\nu) &\mapsto& (\cs{L},\mu,i\der^*(\nu)).
\end{array}
\]
Define $j\times\id_G: G\der\times G\to G\times G$ by $j\times\id_G(h,g) = (j(h),g)$.
Then for $(\cs{L},\mu,\beta) \in \CSab(G)$, define $\nu : n^*\cs{L} \to p_n^*\cs{L}$ by
\[
\begin{tikzcd}
& n^* \cs{L} \arrow{dl}{m\circ (j\times\id_G) = n} \arrow{r} & p_n^*\cs{L} &  \\ 
(j\times\id_G)^* m^* \cs{L} \arrow{dr}{(j\times\id_G)^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
& (j\times\id_G)^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & \cs{L}\vert_{G\der}\boxtimes \cs{L} \arrow{ur}{\beta\times 1}
\end{tikzcd}
\]
Then $(\cs{L},\mu,\nu)\in \CSab'(G)$.
It now follows that $\CSab'(G) \to \CSab(G)$ is an equivalence.
\end{proof}

@@

\begin{proof}
Notation as in the proof of Proposition~\ref{prop:CSGabab}.
Consider the following diagram.
%\[
%\begin{tikzcd}
%{} & G\times G \arrow{d}{c} &&&\\
%1 \arrow{r} & H \arrow{r}{j} & G \arrow{r}{q} & G\ab \arrow{r} & 1
%\end{tikzcd}
%\]
%gives
\[
\begin{tikzcd}
\CS(G\der) & \arrow{l}[swap]{j^*} \CS(G) &\arrow{l}[swap]{q^*} 
\CS(G\ab) \arrow{dl}{\text{equiv}}[swap]{q\ab^*} \\
& \CSab(G) \arrow{u}{\text{forget}}  & 
\end{tikzcd}
\]

>>>>

Let $i : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\times G$ by $j(h) = (i(h),1_G)$. \todo{There's some kind of typo here....}
For $(\cs{L},\mu,\nu)\in \CSab'(G)$, $j^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism.
This defines a functor
\[
\begin{array}{rcl}
\CSab'(G) &\to& \CSab(G) \\
(\cs{L},\mu,\nu) &\mapsto& (\cs{L},\mu,j^*(\nu)).
\end{array}
\]
Define $k: G\der\times G\to G\times G$ by $k(h,g) = (i(h),g)$.
Then for $(\cs{L},\mu,\beta) \in \CSab(G)$, define $\nu : n^*\cs{L} \to p_n^*\cs{L}$ by
\[
\begin{tikzcd}
& n^* \cs{L} \arrow{dl}{m\circ k = n} \arrow{r} & p_n^*\cs{L} &  \\ 
k^* m^* \cs{L} \arrow{dr}{k^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
& k^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & \cs{L}\vert_{G\der}\boxtimes \cs{L} \arrow{ur}{\beta\times 1}
\end{tikzcd}
\]
Then $(\cs{L},\mu,\nu)\in \CSab'(G)$.
It now follows that $\CSab'(G) \to \CSab(G)$ is an equivalence.
\end{proof}

@@

\begin{proof}
Notation as in the proof of Proposition~\ref{prop:CSGabab}.
Consider the following diagram.
%\[
%\begin{tikzcd}
%{} & G\times G \arrow{d}{c} &&&\\
%1 \arrow{r} & H \arrow{r}{j} & G \arrow{r}{q} & G\ab \arrow{r} & 1
%\end{tikzcd}
%\]
%gives
\[
\begin{tikzcd}
\CS(G\der) & \arrow{l}[swap]{j^*} \CS(G) &\arrow{l}[swap]{q^*} 
\CS(G\ab) \arrow{dl}{q\ab^*} \\
& \CSab(G) \arrow{u}{\text{forget}}  & 
\end{tikzcd}
\]
